---
title: "HW08: continue developing foofactors"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HW08: continue developing foofactors}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is my Stat 547M HW08, continuing where Jenny left off on the package `foofactors`.

The first function added is the `detect_fac` function that detects a list of factors that should be characters when the number of unique levels is equal to the length of the list. When the above scenario happens, `detect_fac()` will convert the list from a list of factors to a list of characters; if there are some levels that appear more than once, then we do nothing to this list.

```{r}
#install_github("MingWan10/foofactors")
library(foofactors)
fbind(iris$Species[c(1, 51, 101)], PlantGrowth$group[c(1, 11, 21)])
freq_out(iris$Species)
detect_fac(factor(c("a", "b", "c")))
```

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
